MSstatsPTM statistical relative quantification of post-translational modifications in bottom-up proteomic experiments

### 2022-05-29 main/MSstatsPTM_Main.tex
Small - Fig 4

\begin{figure}[ht]
\centering
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/sim1_FDR_all_models.png}
\caption{}
\label{fig:sim1_fdr}
\end{subfigure}
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/sim3_Accuracy.png}
\caption{}
\label{fig:sim2_acc}
\end{subfigure}
\caption{Dataset 1 \& 2: Computer simulation. a) All the considered methods in the first computer simulation correctly calibrated FDR when adjusting for changes in protein abundance. In comparison, the methods without accounting for the protein-level changes resulted in off-target, high false positive rates. b) The advantage of using the proposed approach was apparent when including limited observations and missing values. Looking at accuracy, the proposed method outperformed Limma and $t$-test in nearly every model.
}
\label{fig:computer_sim}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/sim1_FDR_all_models.png}
\caption{}
\label{fig:sim1_fdr}
\end{subfigure}
\begin{subfigure}[c]{0.825\linewidth}
\includegraphics[width=1\textwidth]{images/sim3_Accuracy.png}
\caption{}
\label{fig:sim2_acc}
\end{subfigure}
\caption{Dataset 1 \& 2: Computer simulation. \todo{OV: in (a) could you use the same color scheme for the methods as in the remaining figures? Use different fill/opacity/shade of a same color for methods with and without the adjustment} a) All the considered methods in the first computer simulation correctly calibrated FDR when adjusting for changes in protein abundance. In comparison, the methods without accounting for the protein-level changes resulted in off-target, high false positive rates. b) The advantage of using the proposed approach was apparent when including limited observations and missing values. Looking at accuracy, the proposed method outperformed Limma and $t$-test in nearly every model.
}
\label{fig:computer_sim}
\end{figure}
